Facotrs Influence Stress in Canada

### 2022-03-19 outputs/paper/paper.Rmd
final commit

More and more Canadian social and economic issues have led to many discussions about the relationship between work, lifestyle, and well-being. Although people are enjoying the conveniences from a technology high-quality life from economic growth, they face much pressure at the same time and even feel less happy than before. (Testing and modeling the fatigue behavior of GFPR composites, Wahid Ferdous, 2020) How to balance life and work in a competitive environment becomes a serious problem. Canadians are encouraged to assess and evaluate their stress level because the government can take actions to increase people’s well-being and decrease their pressure according to their responses. People’s healthy mental condition is beneficial to national growth. Our aim is to help the Canadian government further understand what the characteristics of stressed people are and how to reduce their stress.

@@

```{r tablestress, echo=FALSE,message=FALSE,warning=FALSE}

@@

clean_data %>% 
  datasummary_skim(type = "categorical",
                   title = "Summary of categorical economic indicator 
                   variables for four countries")

@@

```{r piegraph,warning=FALSE,message=FALSE,echo = FALSE}
names = c("Work", 
          "Financial concerns", 
          "Family", 
          "School work", 
          "Not enough time", 
          "Own health", 
          "Other" )

@@

@@

# calculate the percentage
piepercent = paste(round(100*y2/sum(y2)), "%")
piefemale <-pie(y2, 
              labels=piepercent,
              col = rainbow(length(y2)), 
              main ="Main source of stress for female")
```

```{r hours,warning=FALSE,message=FALSE,echo = FALSE}
Name = c("0-15 hours", 
         "16-29 hours", 
          "30 to 40 hours", 
          "Over 41 hours")
h1 <- sum(clean_data$hours_worked =='1') 
h2 <- sum(clean_data$hours_worked =='2')
h3 <- sum(clean_data$hours_worked =='3')
h4 <- sum(clean_data$hours_worked =='4')

@@

```{r alcohol,warning=FALSE,message=FALSE,echo = FALSE}
# create a function to arrange elements alphabetically

ggplot(clean_data,
       aes(x=stress,
           fill = factor(alcohol_consumption, 
                         levels =c("1","2","3","4","5","6","7"),
                         labels = c("Everyday",
                                    "4-6 times a week",
                                    "2-3 times a week",
                                    "Once a week",
                                    "Once or twice in the past month",
                                    "Not in the past month","Never")))
       ) +
geom_bar(position = "stack") +
labs(x="stress level",
     fill="Alcohol consumption",
     title="Alcohol consumption and stress level") +
coord_flip() +
theme_minimal()

@@

```{r smoking,warning=FALSE,message=FALSE,echo = FALSE}
ggplot(clean_data,
       aes(x=stress,
           fill= factor(smoking_status,
                        levels =c("1","2","3"),
                        labels = c("Daily",
                                    "Occasionally",
                                    "Not at all")))
       )+
geom_bar(position = "stack") +
labs(x="stress level",
     fill="Smoking status",
     title="Smoking status and stress level") +
coord_flip() +
theme_minimal()
```

```{r satisfaction,warning=FALSE,message=FALSE,echo = FALSE}
ggplot(clean_data, 
       aes(x = stress, 
           fill = factor(job_satisfaction))) + 
geom_bar(position = "dodge") +
labs(x="stress level",
     fill="Job satisfaction",
     title="Job satisfaction and stress level")

ggplot(clean_data, 
       aes(x = stress, 
           fill = factor(personal_relationship_level))) + 
geom_bar(position = "dodge") +
labs(x="stress level",
     fill="Personal relationships",
     title="Personal relationships and stress level")
```

```{r regression, warning=FALSE,message=FALSE,echo = FALSE}

@@

modelsummary(regression_model)
```

@@

From figure \@ref(fig:satisfaction), we can conclude that job satisfaction and personal relationship are negatively correlated with stress. people are satisfied with their job and confident about their personal relationships usually not bothered by stress.

>>>>

More and more Canadian social and economic issues have led to many discussions about the relationship between work, lifestyle, and well-being. Although people are enjoying the conveniences from a technology high-quality life from economic growth, they face much pressure at the same time and even feel less happy than before. How to balance life and work in a competitive environment becomes a serious problem. Canadians are encouraged to assess and evaluate their stress level because the government can take actions to increase people’s well-being and decrease their pressure according to their responses. People’s healthy mental condition is beneficial to national growth. Our aim is to help the Canadian government further understand what the characteristics of stressed people are and how to reduce their stress.

@@

```{r tablestress,echo=FALSE,message=FALSE,warning=FALSE}

@@

clean_data %>% 
  datasummary_skim(type = "categorical",
                   title = "Summary of categorical 
                   variables")

@@

```{r piegraph,fig.cap="Main source of stress",warning=FALSE,message=FALSE,echo = FALSE}
names = c("Work", 
          "Financial concerns", 
          "Family", 
          "School work", 
          "Not enough time", 
          "Own health", 
          "Other" )

@@

```{r piegender, fig.cap="Main source of stress for male and female",warning=FALSE,message=FALSE,echo = FALSE}

@@

# calculate the percentage
piepercent = paste(round(100*y2/sum(y2)), "%")
piefemale <-pie(y2, 
              labels=piepercent,
              col = rainbow(length(y2)), 
              main ="Main source of stress for female")

```{r hours,fig.cap="Number of hours worked per week at job",warning=FALSE,message=FALSE,echo = FALSE}
Name = c("0-15 hours", 
         "16-29 hours", 
          "30 to 40 hours", 
          "Over 41 hours")
h1 <- sum(clean_data$hours_worked =='1') 
h2 <- sum(clean_data$hours_worked =='2')
h3 <- sum(clean_data$hours_worked =='3')
h4 <- sum(clean_data$hours_worked =='4')

@@

```{r alcohol,fig.cap="Alcohol consumption and stress level",warning=FALSE,message=FALSE,echo = FALSE}

ggplot(clean_data,
       aes(x=stress,
           fill = factor(alcohol_consumption, 
                         levels =c("1","2","3","4","5","6","7"),
                         labels = c("Everyday",
                                    "4-6 times a week",
                                    "2-3 times a week",
                                    "Once a week",
                                    "Once or twice in the past month",
                                    "Not in the past month","Never")))
       ) +
geom_bar(position = "stack") +
labs(x="stress level",
     fill="Alcohol consumption") +
coord_flip() +
theme_minimal()

@@

```{r smoking,fig.cap="Smoking status and stress level",warning=FALSE,message=FALSE,echo = FALSE}
ggplot(clean_data,
       aes(x=stress,
           fill= factor(smoking_status,
                        levels =c("1","2","3"),
                        labels = c("Daily",
                                    "Occasionally",
                                    "Not at all")))
       )+
geom_bar(position = "stack") +
labs(x="stress level",
     fill="Smoking status") +
coord_flip() +
theme_minimal()
```

```{r satisfaction,fig.cap="Job satisfaction and stress level",warning=FALSE,message=FALSE,echo = FALSE}
ggplot(clean_data, 
       aes(x = stress, 
           fill = factor(job_satisfaction))) + 
geom_bar(position = "dodge") +
labs(x="stress level",
     fill="Job satisfaction")
```

```{r relationship,fig.cap="Personal relationship and stress level",warning=FALSE,message=FALSE,echo = FALSE}
ggplot(clean_data, 
       aes(x = stress, 
           fill = factor(personal_relationship_level))) + 
geom_bar(position = "dodge") +
labs(x="stress level",
     fill="Personal relationships")
```

```{r regression,fig.cap="Personal relationship and stress level",warning=FALSE,message=FALSE,echo = FALSE}

@@

modelsummary(regression_model,
             title = "Linear regression model of stress level")
```

@@

From figure \@ref(fig:satisfaction) and figure \@ref(fig:relationship), we can conclude that job satisfaction and personal relationship are negatively correlated with stress. people are satisfied with their job and confident about their personal relationships usually not bothered by stress.
